---
title: "Your Project Title"
author: "Samira Shirazy, Rebecca Chan, Dinah Bahta and Emily Olshan"
date: "2/18/2022"
output: html_document
---

``` {r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
getwd()
# Load necessary libraries
library(knitr)

```

``` {r, echo = FALSE, include = FALSE}
source("../source/line_chart.R")
```

This is a line chart that displays the total homeless population in the United States from the year 2007 to 2016. The purpose of this chart is to show the change in the population from year to year. The data collected shows that homelessness has not been consistent, in other words, it fluctuates. The advantage of the line chart is that the slope can easily be taken between two years to calculate the change. In addition, low and high populations
```{r, echo = FALSE, message = FALSE}
plot(line_chart)
```

``` {r, echo = FALSE, include = FALSE}
source("../source/bar_chart.R")
```

``` {r, echo = FALSE, message = FALSE}
plot(final_bar_chart)
```

``` {r, echo = FALSE, message = FALSE, include = FALSE}
source("../source/Scatter_Plot.R")
```

``` {r, echo = FALSE, message = FALSE}
plot(scatter_plot)
```

``` {r, echo = FALSE, message = FALSE, include = FALSE}
source("../source/summary.R")
```
We combined our 3 datasets in order to look at more years worth of data on homeless populations. This created a combined set of `r summary$num_observations` observations, each representing a different homeless population at a specific point in time. The area with the highest total homeless population was `r summary$area_highest_total` and the state with the highest total homeless population was `r summary$state_highest_total_2018`. Many of our research questions have to do with the different situations of homeless individuals, such as whether they are sheltered or not. The average percent by state of homeless individuals who were sheltered was `r summary$avg-percent-sheltered-2016`% and unsheltered individuals averaged `r summary$avg-percent-unsheltered-2016`%

``` {r, echo = FALSE, message = FALSE, include = FALSE}
source("../source/aggregate_table.R")
```
In this table, we averaged the percent of individuals who were sheltered or unsheltered in 2016 by state. We chose to show this information because a lot of our questions have to do with the trends in different situations across areas and time. This is simply an example of that.
``` {r, echo = FALSE, message = FALSE}
kable(sheltered_unsheltered_by_state)
```